---
title: "clocks1"
author: "Rathin Sinha"
date: "25/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
data("ToothGrowth")
summary(ToothGrowth)
```


```{r}
head(ToothGrowth)
unique(ToothGrowth$len)
unique(ToothGrowth$supp)
unique(ToothGrowth$dose)
...


```{r}
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=dose)) + xlab("Dose Amount") + ylab("Tooth Length") + facet_grid(~ supp) + ggtitle("Tooth Length vs. Dose Amount \nby Delivery Method") + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp)) + xlab("Supplement Delivery") + ylab("Tooth Length") + facet_grid(~ dose) + ggtitle("Tooth Length vs. Delivery Method \nby Dose Amount") + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
t.test(len~supp,data=ToothGrowth)
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(1.0,0.5))
t.test(len~dose,data=ToothGrowth_sub)
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(0.5,2.0))
t.test(len~dose,data=ToothGrowth_sub)
ToothGrowth_sub <- subset(ToothGrowth, ToothGrowth$dose %in% c(1.0,2.0))
t.test(len~dose,data=ToothGrowth_sub)


Assumptions:
  1)sample is that of population
  2)Central limit theorem

Conclusion:increased dosages results in increased tooth length
